% Changes ot test overleaf sync

%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT    
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }





%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Nuria Máñez Molina} \\[7.5pt]
\href{mailto:manezmolinanuria@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ manezmolinanuria@gmail.com} \ $|$ \ 
\href{tel:+4561448151}{\raisebox{-0.05\height}\faMobile \ +4561448151} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
Engineering student at DTU specializing in Cyber Systems with experience as a Teaching Assistant in statistics, cyber systems, and mathematics. Skilled in programming, problem-solving, and communication, with hands-on project and research experience. Background in hospitality strengthened leadership and time management. Passionate about data-driven problem solving, computational methods, and impactful projects.

%Experience
\section{Work Experience}

\begin{joblong}{DTU Teaching Assistant}{February 2025 - Present}
\item \textbf{Statistics:} Assisted in exercise sessions and projects, guiding students with probability, hypothesis testing, and regression models while strengthening my skills in communication, mentoring, and technical expertise. Also supported the design of exercises and graded assignments.
\item \textbf{Introduction to Cyber Systems:} Supported lab sessions on hardware and software, assisting students in simulations, coding exercises, and project development. Enhanced teamwork and mentoring abilities, along with technical expertise in cyber systems.
\item \textbf{Advanced Engineering Mathematics II:} Helped students with advanced calculus, linear algebra, and differential equations, providing problem-solving support in tutorials and feedback on assignments. Further developed collaboration, communication, and applied mathematics expertise.
\end{joblong}\\\\
\begin{joblong}{Polyteknisk Forening (DTU)}{August 2025 - Present}
\item Worked in a student cafe at DTU, delivering friendly and efficient service to students and staff in a university environment.
\item Handled cash register operations, food and beverage preparation, and daily cafe operations while maintaining hygiene and quality standards.
\item Collaborated with a student team to ensure smooth shifts, strong workflow, and a welcoming atmosphere.
\item Worked as a bartender during events, ensuring efficient service and a positive guest experience.
\item Developed skills in teamwork, responsibility, communication, and time management in a fast-paced setting.
\item Was part of the well-being committee, making a better environment for workers and helping the management team.
\end{joblong}
\\
\begin{joblong}{Tango y Vinos ApS}{December 2023 - August 2025}
\item Delivered excellent customer service in a fast-paced restaurant, ensuring a welcoming and professional guest experience.  
\item Managed floor operations, trained and supervised staff, and supported events such as wine tastings to enhance customer satisfaction and boost sales.  
\item Built expertise in leadership, teamwork, time management, communication, and hospitality, including barista and cocktail service.  
\end{joblong}\\\\
\begin{joblong}{ONETEN Providence}{October 2023 - February 2024}
\item Assisted in front-of-house service, welcoming guests and ensuring a smooth dining experience.  
\end{joblong}\\
\begin{joblong}{Il-Matarello}{August 2023 - October 2023}
\item Worked as part of a small team in an authentic Italian restaurant, providing attentive and customer-focused service.  
\end{joblong}
\newpage
%Education
\section{Education}
\begin{joblong}{BSc in General Engineering, Technical University of Denmark (DTU)}{2023 -- 2026}
\begin{itemize}
    \item Specialization in Cyber Systems, with coursework in software development, applied mathematics, and computational methods.  
    \item Participated in software projects and group-based design-build activities, strengthening technical skills, teamwork, and project management.  
    \item Gained experience in multiple programming languages including Python, F#, R, Java, and Julia.  
    \item Strong academic interest in mathematics, statistics, and problem solving.  
    \item Aspiring to pursue a Master’s degree in Business Analytics, with a focus on applied mathematics, data science, and project-driven research.  
\end{itemize}
\end{joblong}
\begin{joblong}{Science Baccalaureate, IES Alto Palancia (Segorbe, Spain)}{2021 -- 2023}
\begin{itemize}
    \item Completed a Science Baccalaureate with a focus on mathematics, physics, and chemistry.  
    \item Graduated with Highest Honors, recognizing academic excellence and outstanding performance.  
\end{itemize}
\end{joblong}
\section{Projects}
\begin{joblong}{Design-Built Projects (DTU)}{Honourable Mention}
\begin{itemize}
  \item Completed four hands-on engineering builds integrating theory with practical implementation.
  \item Recognized by faculty for outstanding performance.
\end{itemize}
\end{joblong}
\begin{joblong}{Science, Technology and Society (DTU)}{}
\begin{itemize}
  \item Researched how technology shapes society; delivered collaborative presentations.
  \item Co-authored a course paper, strengthening academic writing and analysis.
  \item Built critical thinking and communication in an interdisciplinary context.
\end{itemize}
\end{joblong}
\begin{joblong}{Group Mediation}{}
\begin{itemize}
  \item Facilitated teamwork and conflict resolution in a group mediation project.
  \item Ensured effective collaboration through structured group facilitation.
\end{itemize}
\end{joblong}
\begin{joblong}{Children's Activity and Summer Program}{}
\begin{itemize}
  \item Organized activities and provided care in a community program for children.
  \item Demonstrated responsibility, creativity, and leadership through social engagement.
\end{itemize}
\end{joblong}
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Programming \& Technical} & Python, F\#, R, Java, Julia\\
\textbf{Data \& Analysis} & \normalsize{Statistical modeling, Numerical methods, Computational problem solving, Data visualization} \\
\textbf{Software Tools} & Microsoft Office 365 (Excel, Word, PowerPoint), LaTeX, Git \\
\textbf{Collaboration Tools} & Microsoft Teams, SharePoint, OneDrive, Outlook \\
\textbf{Organizational Skills} & Project planning, Structured problem solving, Time management, Group facilitation, Leadership \\
\textbf{Work Ethic} & Proactive, Detail-oriented, Structured, and Team-focused \\
\textbf{Languages} & \normalsize{English (Fluent, C1), Spanish and Catalan (Native), French (Basic, A2) and Danish (Basic, A2+)} \\
\end{tabularx}



\end{document}
